---
title: "Measures of central tendency"
author: "OscarPerez"
date: "4/20/2021"
output: html_document
---
```{r echo=FALSE}
#Oscar Alfredo Perez Ramirez 20 April 2021
#Import the dataset in RStudio
```

## Measures of central tendency and measures of variability and the relationships for "**rating**"
```{r rating}
View(attitude)
mean(attitude$rating)
median(attitude$rating)
mode(attitude$rating)
max(attitude$rating)
min(attitude$rating)
range(attitude$rating)
quantile(attitude$rating)
IQR(attitude$rating)
var(attitude$rating)
sd(attitude$rating)
```
## Measures of central tendency and measures of variability and the relationships for "**complaints**"

```{r complaints}
mean(attitude$complaints)
median(attitude$complaints)
mode(attitude$complaints)
max(attitude$complaints)
min(attitude$complaints)
range(attitude$complaints)
quantile(attitude$complaints)
IQR(attitude$complaints)
var(attitude$complaints)
sd(attitude$complaints)
```
## Measures of central tendency and measures of variability and the relationships for "**privileges**"

```{r privileges}
mean(attitude$privileges)
median(attitude$privileges)
mode(attitude$privileges)
max(attitude$privileges)
min(attitude$privileges)
range(attitude$privileges)
quantile(attitude$privileges)
IQR(attitude$privileges)
var(attitude$privileges)
sd(attitude$privileges)
```
## Measures of central tendency and measures of variability and the relationships for "**learning**"

```{r learning}
mean(attitude$learning)
median(attitude$learning)
mode(attitude$learning)
max(attitude$learning)
min(attitude$learning)
range(attitude$learning)
quantile(attitude$learning)
IQR(attitude$learning)
var(attitude$learning)
sd(attitude$learning)
```
## Measures of central tendency and measures of variability and the relationships for "**raises**"

```{r raises}
mean(attitude$raises)
median(attitude$raises)
mode(attitude$raises)
max(attitude$raises)
min(attitude$raises)
range(attitude$raises)
quantile(attitude$raises)
IQR(attitude$raises)
var(attitude$raises)
sd(attitude$raises)
```

## Measures of central tendency and measures of variability and the relationships for "**critical**"

```{r critical}
mean(attitude$critical)
median(attitude$critical)
mode(attitude$critical)
max(attitude$critical)
min(attitude$critical)
range(attitude$critical)
quantile(attitude$critical)
IQR(attitude$critical)
var(attitude$critical)
sd(attitude$critical)
```

## Measures of central tendency and measures of variability and the relationships for "**advance**"

```{r advance}
mean(attitude$advance)
median(attitude$advance)
mode(attitude$advance)
max(attitude$advance)
min(attitude$advance)
range(attitude$advance)
quantile(attitude$advance)
IQR(attitude$advance)
var(attitude$advance)
sd(attitude$advance)
```

## **Summary**


```{r}
summary(attitude)
cor(attitude)
plot(attitude)
library(car)
scatterplot(attitude$rating,attitude$complaints,xlab="Rating", ylab="Complaints", main="Highest correlation", smooth=FALSE)
```
